Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-06-11 manuscript.Rmd

In addition to post-processing original article records, R was also used for
all other data analysis.  R is an ideal analytic tool because it is
open-source and has a suite of related tools for producing reproducible
research.  More specifically, all the source code is written using Rmarkdown --
an open-source system that integrates data management, data analysis, and the
written report.  The source code and data extracts are also curated at openICPSR
of the Inter-university Consortium for Political and Social Research of the
University of Michigan.  The source code is also available from the first
author's GitHub repository, where the code will be maintained and updated to
support future research projects. It should be noted that the full data files
cannot be made publicly available because these are considered proprietary data
of the database services.  However, to ensure full compliance with the best
practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affiliated with an institution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.  This is designed to meet an ethic of maximum allowable data transparency while respecting the proprietary nature of the data.

# Results
```{r}
# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.  The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`). The overall h-Index for each journal.  The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.  The mean h-Index value is XXXX, (median = XXX; sd = XXX). A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.  The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`). This figure shows consistent growth in the number of articles from 1989 to 2005.  Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012. The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.  
```

### Aggregated summary (Figure 1a. 1b. -- line charts)

>>>>

In addition to post-processing original article records, R was also used for all
other data analysis.  R is an ideal analytic tool because it is open-source and
has a suite of related tools for producing reproducible research.  More
specifically, all the source code is written using Rmarkdown -- an open-source
system that integrates data management, data analysis, and the written report. 
The source code and data extracts are also curated at openICPSR of the
Inter-university Consotrium for Political and Social Research of the University
of Michigan.  The source code is also available from the first author's GitHub
repository, where the code will be maintained and updated to support future
research projects. It should be noted that the full data files cannot be made
publicly available because these are considered proprietary data of the database
services.  However, to ensure full compliance with the best practices of
reproducible research (cite King), we have provided the journal editor with the
following conditions under which we would release the data: (1) the requester
must be affilitated with an insitution that provides access to both the
EbscoHost and ProQuest platforms along with the databases used in this study or
(2) hold a personal subscription to each platform and the databases utilized
here.  This is designed to meet the standards of maximum allowable data
transparency while respecting the proprietary nature of the data.

# Results

We collected a total of 3X,XXX article records from XX different databases.  Extensive cleaning procedures were applied to exclude documents that were not filtered in the original retrieval process.  More specifically, as described in the Methods section, we filtered documents to include only journals, while excluding editorials, book reviews, table of contents, and other documents that are not considered journal articles.  This reduced the total number of unique article records in the database to xx,xxxx.

## Size and growth of social work
